%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Architect} % Job title
    {Saongroup} % Organization
    {San Salvador, El Salvador} % Location
    {January 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Designed and led the migration of our monolithic applications into microservices. Conceptualized and built in collaboration with senior developers an internal microservice framework to make adoption of microservice easier and seamlessly enforce microservice guidelines.
        }
        \item {
          Designed the global frontend architecture, implemented and standardized
          the frontend of all company products through a React design system and React
          components library that was used by all developers, significantly reducing efforts
          required to implement UI changes and improving the user experience.
        }
        \item {
          Transformed the application lifecycle of the company by integrating
          DevOps practices when the company had none. Moved from a classic CI to
          a Continuous Delivery approach. Reduced cycle times and increased
          deployment frequency while reducing release rollbacks at the same time.
        }
        \item {
          Led the adoption of serverless architecture. Designed the CI/CD serverless pipelines. Established serverless architecture guidelines to reduce adoption friction. Built libraries tailored to the company needs for serverless adoption. Mentored developers on Serverless framework and SAM CLI. After adoption AWS static server costs were reduced and maintenance required to operate API's was reduced.
        }
        \item {
          Formed and led platform engineering team. Delivered various technical
          products to increase the productivity of the development team, such as
          a custom CLI to automate generation of boilerplates, a microservice
          framework that took care fo common concerns and allowed the developers
          to focus on the business logic.
        }
        \item {
          Formed Devops and Test Automation teams. Responsible for DevOps
          strategy implementation. Designed automation strategy, led automation team.
        }
      \end{cvitems}
    }
    {
      \begin{cventrysummary} % Summary statement
        Responsible for technical strategy and architecture. Oversaw
        architectural design of 5 teams of 4 developers, ensuring that teams
        wrote maintainable and testable code. Acted as program
        manager for technical projects. Responsible for technical recruitment
        and hiring of over 30 developers.
      \end{cventrysummary}
    }

%---------------------------------------------------------
  \cventry
    {Technical Lead} %Job title
    {Saongroup}
    {San Salvador, El Salvador}
    {January 2011 - December 2015} % Date
    {
      \begin{cvitems}
        \item {Led and co-developed the migration of various complex legacy web applications successfully to the .NET platform. Technical debt, and maintenance costs reduced significantly after migrations. All delivered on time.}
        \item {Designed a common technology platform for all web applications of the company, reducing the time to implement new features across company products.}
        \item {Introduced continuous integration: Migrated from TFS to Git. Setup pipelines in Bamboo, and configured automated deployments to production.}
      \end{cvitems}
    }
    {Led a growing engineering team of 5 developers. Grew the team to 25 developers. Responsible for planning, mentorning and leadership. Used ASP.NET MVC and C\#.}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Equifax} % Organization
    {San Salvador, El Salvador} % Location
    {February 2010 - December 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the architecture of the application.}
        \item {Implemented design patterns to make the application easier to maintain}
        \item {Responsible for technical training to the client’s development team and deployments done monthly in the client’s Panama office}
      \end{cvitems}
    }
    {Led and developed a loan origination application for a high profile client in Panama in C\# and ASP.NET. Project duration was a year.}

%---------------------------------------------------------
  % \cventry
  %   {Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
  %   {R.O.K Cyber Command, MND} % Organization
  %   {Seoul, S.Korea} % Location
  %   {Aug. 2014 - Apr. 2016} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
  %       \item {Implemented a distributed web stress test tool with high anonymity.}
  %       \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
  %     \end{cvitems}
  %   }
  %   {}

%---------------------------------------------------------
  % \cventry
  %   {Game Developer Intern at Global Internship Program} % Job title
  %   {NEXON} % Organization
  %   {Seoul, S.Korea \& LA, U.S.A} % Location
  %   {Jan. 2013 - Feb. 2013} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
  %       \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
  %       \item {Won the 2nd prize in final evaluation.}
  %     \end{cvitems}
  %   }
  %   {}

%---------------------------------------------------------
  % \cventry
  %   {Software Engineer} % Job title
  %   {ShitOne Corp. (Start-up company)} % Organization
  %   {Seoul, S.Korea} % Location
  %   {Dec. 2011 - Feb. 2012} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
  %       \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
  %       \item {•	Introduced continuous integration: Migrated from TFS to Git. Setup pipelines in Bamboo, and configured automated deployments to production.}
  %     \end{cvitems}
  %   }
  %   {}

%---------------------------------------------------------
  % \cventry
  %   {Freelance Penetration Tester} % Job title
  %   {SAMSUNG Electronics} % Organization
  %   {S.Korea} % Location
  %   {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
  %       \item {Conducted penetration testing on SAMSUNG Smart TV.}
  %     \end{cvitems}
  %     %\begin{cvsubentries}
  %     %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
  %     %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
  %     %\end{cvsubentries}
  %   }
  %   {}

%---------------------------------------------------------
\end{cventries}
